---
title: "EDS212 Day5a"
author: "Rachel Swick"
format: html
execute: 
  warning: false
---

##Hi its Amanda :)

```{r}
#| message: false
# load libraries ----
library(tidyverse)
```

Try using `head()`, `tail()`, and `dim()` on the `dplyr::starwars` data frame:

```{r}
#| include: false
# do some data exploration on the starwars df ----
head(starwars, n = 5)
tail(starwars, n = 10)
dim(starwars)
```

- Create a ggplot (scatterplot) of character `mass` (y-axis) and `height` (x-axis)
- update the color of the points so that color changes based on the value of `mass`

```{r}
#| echo: false
ggplot(data = starwars, aes(x = height, y = mass, color = mass)) +
  geom_point() +
  labs(title = "Starwars Character Height and Weights") +
  labs(x = "Height (cm)", 
       y = "Mass (kg)")
```

- Create a histogram of character heights
- Update the fill color (`fill`) to purple and the outside border line (`color`) of each histogram bin to orange
- Update your code chunk options so that only your code and output graph appear in the rendered doc (no warnings or messages)
- Update the axis labels

```{r}
#| fig-cap: "Figure 1. This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(data = starwars, aes(x = height))+
  geom_histogram(color = 'orange', fill = 'purple')+
  labs(x = "Height (cm)",
       y = "Number of Characters")+
  labs(title = "Figure 1. Histogram of Starwars Character Heights")
```

`df$col_name` - this is the command to call a particular column from a df

```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), 3)
sw_height_mean
```

The mean height of all starwars characters is `r sw_height_mean`












